Bayesian exponential random graph modeling of KWL Burial network

### 2020-10-29 analysis/paper/paper.Rmd
edit Intro, adjust model, and add references

<!--burial study- network analysis-->
Burials contain valuable information about both individual mortuary practices and the structure of a society . The development of network science and graph theory provides many new tools for the study of the relations between burials and exploration their social implications [@Sosna2013]. Mortuary practices such as burial forms, grave goods, and related ritual practices that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [citation needed]. This means we can use data from burials to study social differences to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For example, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs. Burials with grave goods in common often indicate some similar underlying social relations, for example, individuals that share similar access to trade, exchange, and gifting networks [@Coward2013, pp. 252]. Identifying the structure of relationships among burials can give insights into the structure of social organization.

One common way to study connections between individuals is network analysis, which has been increasingly applied by archaeologists in recent years [@Mills2017]. Networks are represented as graphs consisting of a set of actors, such as people, groups, or organizations, and a set of links connecting them [@Brughmans2018; @Robins2007]. <!-- define 'links' a bit more --> Actors are "nodes" connected by multiple "edges", representing relationships, between nodes. The basic unit of relationship is called a dyad, defined as a connection between two distinct actors [@Lee2016]. In archaeology, relationships can be viewed as flows of resources that reflect relations of control, dependence, and cooperation, indicating social relations in societies [@Marin2011]. With network analysis, we can quantify, visualize, and statistically test hypotheses about the relationships between actors to examine the structure of network and major factors that affect the formation of the structure [@Freeman2004; @Salvini2010]. Network analysis in archaeology is widely used for different topics including distribution of archaeological sites, grave goods, and social complexity [@Coward2013; @Mizoguchi2013; @Potgieter2008]

>>>>

<!--burial study- network analysis-->
Burial analysis has long developed in archaeology to study societies through mortuary practices, such as cultural and biological records in burial contexts, reflecting the social status or identity of the deceased [@Binford1971; @Saxe1970]. This approach is criticized for its simple connection between real life in society and death expression without considering the manipulation of the living or distortion [@Hodder1980; @Pearson1982]. However, quantitative analysis for burial data is still an effective way to answer questions related to social representations with both social representation for death and life in mind [@Chapman2003]. Mortuary practices include burial forms, grave goods, and related ritual practices that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [@Byrd1995; @Seikel2011]. The development of network science and graph theory provides many new tools for the study of the relations between burials and exploration their social implications [@Sosna2013]. This means we can use data from burials to study social differences to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For example, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs. Burials with grave goods in common often indicate some similar underlying social relations, for example, individuals that share similar access to trade, exchange, and gifting networks [@Coward2013, pp. 252]. Identifying the structure of relationships among burials can give insights into the structure of social organization.

One common way to study connections between individuals is network analysis, which has been increasingly applied by archaeologists in recent years [@Mills2017]. Networks are represented as graphs consisting of a set of actors, such as people, groups, or organizations, and a set of links representing relationship, such as friendships, connecting them [@Brughmans2018; @Robins2007]. Actors are "nodes" connected by multiple "edges", representing relationships, between nodes. The basic unit of relationship is called a dyad, defined as a connection between two distinct actors [@Lee2016]. In archaeology, relationships can be viewed as flows of resources that reflect relations of control, dependence, and cooperation, indicating social relations in societies [@Marin2011]. With network analysis, we can quantify, visualize, and statistically test hypotheses about the relationships between actors to examine the structure of network and major factors that affect the formation of the structure [@Freeman2004; @Salvini2010]. Network analysis in archaeology is widely used for different topics, such as exploring hunter-gatherer exchange network in the Kuril Islands based on ceramic compositions [@Erik2015]; [@Coward2013; @Mizoguchi2013; @Potgieter2008].

ore specifically, this research constructs network models from the compositional analysis of ceramic artifacts recovered in the Kuril Islands of northeast Asia and evaluates network centrality measures using bootstrap simulation and sensitivity analysis. Results of this research suggest that while archaeologists may never fully identify the "true" network of past relationships, network models that approximate "true" network structure can provide useful metrics in exploring the behavior of past hunter-gatherer populations. Overall, given the challenges associated with hunter-gatherer archaeological data, it is argued here that critically evaluating the structure and stability of network models is an essential first step in developing an archaeological network analysis that is relevant and informative to research on past small-scale societies.
